### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@f14ca88f84fed5da917f3bce816a15f3c9be159f 🚀

The existence of well-defined cophylogenetic regions suggests that the
bat-betacoronavirus system is spatially fragmented enough to create
divergent coevolutionary trajectories; in turn, this coevolutionary
mosaic may alter the risk of zoonotic emergence. These ideas are,
respectively, supported by the existence of hotspots of viral uniqueness
and the diverse origins of human betacoronaviruses. Together, this
framework points to a predictable relationship between host community
structure and coevolutionary pressure: phylogeographic structure in bat
hosts (and their diverse immune strategies)\textsuperscript{23} creates
a landscape of selective pressure; the trajectory of viruses'
coevolutionary response is, in turn, constrained by their opportunities
for either coevolutionary specialization or diversification through host
jumps and recombination.

>>>>

The existence of well-defined cophylogenetic regions suggests that the
bat-betacoronavirus system is spatially fragmented enough to create
divergent coevolutionary trajectories; in turn, this coevolutionary
mosaic may alter the risk of zoonotic emergence. These ideas are,
respectively, supported by the existence of hotspots of viral uniqueness
and the diverse origins of human betacoronaviruses. Together, this
framework points to a predictable relationship between host community
structure and coevolutionary pressure: phylogeographic structure in bat
hosts (and their diverse immune strategies)\textsuperscript{23} creates
a landscape of selective pressure; the trajectory of viruses'
coevolutionary response is, in turn, constrained by their opportunities
for either specialization or diversification through host jumps and
recombination.
